Reproducible and programmatic generation of neuroimaging visualizations

### 2022-04-23 manuscript.Rmd
test
.

---
title: Reproducible and programmatic generation of neuroimaging visualizations
authors:
  - name: Sidhant Chopra
    thanks: Corresponding author
    department: Department of Psychology
    affiliation: Yale University
    location: CT, USA, 06511
    email: sidhant.chopra@yale.com
  - name: Loïc Labache
    department: School of Psychology
    affiliation: Department of Psychology
    location: CT, USA, 06511
  - name: Edwina R Orchard
    department: School of Psychology
    affiliation: Department of Psychology
    location: CT, USA, 06511
  - name: Avram Holmes
    department: School of Psychology
    affiliation: Department of Psychology
    location: CT, USA, 06511
abstract: Add words here. 
keywords:
  - Brain Visualization
  - MRI Visualization
output: 
  bookdown::pdf_book:
    base_format: rticles::arxiv_article
    keep_tex: true
    latex_engine: xelatex
  bookdown::word_document2:
    toc: false
linestretch: 2
header-includes:
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \usepackage{setspace}\doublespacing
---

@@

\

|                                 | Voxel | Vertex | ROI | Edge | Streamlines |
|:--------------------------------|:-----:|:------:|:---:|:----:|:-----------:|
| R                               |       |        |     |      |             |
| ciftitools                      |   ✓   |   ✓    | ✓\* |      |             |
| fsbrain                         |   ✓   |   ✓    | ✓\* |      |             |
| oro.nifti                       |   ✓   |        |     |      |             |
| neurobase                       |   ✓   |        |     |      |             |
| ggseg                           |       |        |  ✓  |      |             |
| brainconn                       |       |        |     |  ✓   |             |
| Python                          |       |        |     |      |             |
| surfice                         |   ✓   |   ✓    |  ✓  |  ✓   |      ✓      |
| nilearn                         |   ✓   |   ✓    |  ✓  |  ✓   |             |
| Visbrain                        |   ✓   |   ✓    |  ✓  |  ✓   |             |
| Pycortex                        |   ✓   |   ✓    | ✓\* |      |             |
| pySurfer                        |       |   ✓    | ✓\* |      |             |
| Brainspace/surfplot             |       |   ✓    | ✓\* |      |             |
| netneurotools                   |       |   ✓    | ✓\* |      |             |
| Brainplotlib                    |       |   ✓    | ✓\* |      |             |
| DIPY                            |   ✓   |        |     |      |      ✓      |
| mrivis                          |   ✓   |        |     |      |             |
| ENIGMA toolbox                  |       |        |  ✓  |      |             |
| ggseg                           |       |        |  ✓  |      |             |
| graphpype                       |       |        |     |  ✓   |             |
| MATLAB                          |       |        |     |      |             |
| Vistasoft                       |   ✓   |   ✓    |  ✓  |      |      ✓      |
| BrainNetViewer                  |   ✓   |        |  ✓  |  ✓   |             |
| mrtools                         |   ✓   |   ✓    | ✓\* |      |             |
| FieldTrip                       |   ✓   |   ✓    |     |      |             |
| ECoG/fMRI visualization toolbox |       |   ✓    | ✓\* |      |             |
| plotSurfaceROIBoundary          |       |   ✓    | ✓\* |      |             |
| Brainspace                      |       |   ✓    | ✓\* |      |             |
| CandlabCore                     |   ✓   |        |  ✓  |      |             |
| ENIGMA toolbox                  |       |        |  ✓  |      |             |

\

@@

@@

Often cerebellar and brain-stem regions are not well represented in software (e.g. Figure 1), potentially mirroring a cortico-centric sentiment that has prevailed in human neuroimaging (Chin, Chang, & Holmes). Likewise, custom regions of interest, such as non-standard subcortical atlas schemes is not yet straight forward, and usually require multiple functions and packages to visualize. Finally, some neuroimaging related data types, such as streamlines resulting from DWI-based tractography, are still not well represented in code-based vizualistion tools.

@@

### Supplement (Code used to generate figure)

@@

#Set the breaks/intervas you want on the color bar (e.g. from .3 to .6, by intervals of 0.005)
breaks = seq(.3,.6, by=0.005)

@@

#Use the ortho2 function from the neurobase package to make the figure
ortho2(x = template,   #Specify the background template
       y = effect,     #Specify the effect you want to overlay on the tempplate
       crosshairs = F, #Remove the cross-hairs
       bg = "white",   #Make the background white 
       NA.x = T,       #Do not display NA values
       col.y= viridis::viridis(n = 500), #Select the colour scale. In this case I have used the viridis scale from the viridis package. 
       xyz = c(70,50,80), #set the x y & z slice you want to visualise
       useRaster = T,   #Sometimes using Raster makes for clearer plots
       ycolorbar = TRUE, #Add a colorbar
       mfrow = c(1,1)) + 
  colorbar(breaks,col = viridis::viridis(n=length(breaks)-1), 
           text.col = "black", labels = TRUE, maxleft = 0.95)  #Set the specifications for the colorbar

@@

library(fsbrain)

@@

colourmap <- colorRampPalette(viridis::viridis(n = 10000))
fsbrain.set.default.figsize(700, 700);

cm = vis.subject.morph.standard(subjects_dir, 
                                subject_id, 'sulc', 
                                fwhm='10', 
                                cortex_only = T, 
                                views=NULL, 
                                makecmap_options = list('colFn'=colourmap))
img = export(cm, colorbar_legend='Effect', output_img = "data/fig1d.png")

rgl.snapshot("data/fig1d.png")
rgl.close()

>>>>

---
title: Reproducible and programmatic generation of neuroimaging visualizations
authors:
  - name: Sidhant Chopra
    thanks: Corresponding author
    department: Department of Psychology
    affiliation: Yale University
    location: CT, USA, 06511
    email: sidhant.chopra@yale.com
  - name: Loïc Labache
    department: Department of Psychology
    affiliation: Yale University
    location: CT, USA, 06511
  - name: Edwina R Orchard
    department: Department of Psychology
    affiliation: Yale University
    location: CT, USA, 06511
  - name: Avram Holmes
    department: Department of Psychology
    affiliation: Yale University
    location: CT, USA, 06511
keywords:
  - Neuroimaging visualization
  - Reproducibility 
  - Programmatic figures
  - Open Science
  - R
output: 
  bookdown::word_document2:
    toc: false
  bookdown::pdf_book:
    base_format: rticles::arxiv_article
    keep_tex: true
    latex_engine: lualatex
linestretch: 2
header-includes:
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \usepackage{setspace}\doublespacing
---

@@

\
**Table 1. Examples of code-based neuroimaging visualizations tools that can be accessed directly within R, MATLAB and Python environments.**

+------------------------+-----------+-----------+-----------+-----------+-------------+
|                        | Voxel     | Vertex    | ROI       | Edge      | Streamlines |
+:=======================+:==========+:==========+:==========+:==========+:============+
| **R**                  |           |           |           |           |             |
+------------------------+-----------+-----------+-----------+-----------+-------------+
|  ANTsR                 | ✓         | ✓         | ✓         |           |             |
+------------------------+-----------+-----------+-----------+-----------+-------------+
| brainconn              |           |           |           | ✓         |             |
+------------------------+-----------+-----------+-----------+-----------+-------------+
| brainR                 | ✓         |           | ✓         |           |             |
+------------------------+-----------+-----------+-----------+-----------+-------------+
| ciftitools             | ✓         | ✓         | ✓\*       |           |             |
+------------------------+-----------+-----------+-----------+-----------+-------------+
| fsbrain                | ✓         | ✓         | ✓\*       |           |             |
+------------------------+-----------+-----------+-----------+-----------+-------------+
| ggseg                  |           |           | ✓         |           |             |
+------------------------+-----------+-----------+-----------+-----------+-------------+
| neurobase              | ✓         |           |           |           |             |
+------------------------+-----------+-----------+-----------+-----------+-------------+
| oro.nifti              | ✓         |           |           |           |             |
+------------------------+-----------+-----------+-----------+-----------+-------------+
| **Python**             |           |           |           |           |             |
+------------------------+-----------+-----------+-----------+-----------+-------------+
| ANTsPy                 | ✓         | ✓         | ✓         |           |             |
+------------------------+-----------+-----------+-----------+-----------+-------------+
| brainiak               | ✓         |           |           |           |             |
+------------------------+-----------+-----------+-----------+-----------+-------------+
| Brainplotlib           |           | ✓         | ✓\*       |           |             |
+------------------------+-----------+-----------+-----------+-----------+-------------+
| Brainspace/surfplot    |           | ✓         | ✓\*       |           |             |
+------------------------+-----------+-----------+-----------+-----------+-------------+
| DIPY                   | ✓         |           |           |           | ✓           |
+------------------------+-----------+-----------+-----------+-----------+-------------+
| ENIGMA toolbox         |           |           | ✓         |           |             |
+------------------------+-----------+-----------+-----------+-----------+-------------+
| FSLeyes                | ✓         | ✓         | ✓         |           |             |
+------------------------+-----------+-----------+-----------+-----------+-------------+
| ggseg                  |           |           | ✓         |           |             |
+------------------------+-----------+-----------+-----------+-----------+-------------+
| graphpype              |           |           |           | ✓         |             |
+------------------------+-----------+-----------+-----------+-----------+-------------+
| MMVT                   |           | ✓         | ✓         | ✓         |             |
+------------------------+-----------+-----------+-----------+-----------+-------------+
| MNE                    | ✓         | ✓         | ✓         |           |             |
+------------------------+-----------+-----------+-----------+-----------+-------------+
| mrivis                 | ✓         |           |           |           |             |
+------------------------+-----------+-----------+-----------+-----------+-------------+
| NaNSlice               | ✓         |           |           |           |             |
+------------------------+-----------+-----------+-----------+-----------+-------------+
| netneurotools          |           | ✓         | ✓\*       |           |             |
+------------------------+-----------+-----------+-----------+-----------+-------------+
| nilearn                | ✓         | ✓         | ✓         | ✓         |             |
+------------------------+-----------+-----------+-----------+-----------+-------------+
| niwidget               | ✓         | ✓         |           |           | ✓           |
+------------------------+-----------+-----------+-----------+-----------+-------------+
| Pycortex               | ✓         | ✓         | ✓\*       |           |             |
+------------------------+-----------+-----------+-----------+-----------+-------------+
| pySurfer               |           | ✓         | ✓\*       |           |             |
+------------------------+-----------+-----------+-----------+-----------+-------------+
| surfice                | ✓         | ✓         | ✓         | ✓         | ✓           |
+------------------------+-----------+-----------+-----------+-----------+-------------+
| surfplot               |           | ✓         | ✓         |           |             |
+------------------------+-----------+-----------+-----------+-----------+-------------+
| Visbrain               | ✓         | ✓         | ✓         | ✓         |             |
+------------------------+-----------+-----------+-----------+-----------+-------------+
| **MATLAB**             |           |           |           |           |             |
+------------------------+-----------+-----------+-----------+-----------+-------------+
| BrainNetViewer         | ✓         |           | ✓         | ✓         |             |
+------------------------+-----------+-----------+-----------+-----------+-------------+
| Brainspace             |           | ✓         | ✓\*       |           |             |
+------------------------+-----------+-----------+-----------+-----------+-------------+
| Brainstorm             | ✓         | ✓         | ✓         |           |             |
+------------------------+-----------+-----------+-----------+-----------+-------------+
| bspmview               | ✓         |           | ✓         |           |             |
+------------------------+-----------+-----------+-----------+-----------+-------------+
| CandlabCore            | ✓         |           | ✓         |           |             |
+------------------------+-----------+-----------+-----------+-----------+-------------+
| ECoG/fMRI Vis toolbox  |           | ✓         | ✓\*       |           |             |
+------------------------+-----------+-----------+-----------+-----------+-------------+
| ENIGMA toolbox         |           |           | ✓         |           |             |
+------------------------+-----------+-----------+-----------+-----------+-------------+
| FieldTrip              | ✓         | ✓         |           |           |             |
+------------------------+-----------+-----------+-----------+-----------+-------------+
| Lead-DBS               | ✓         |           | ✓         |           |             |
+------------------------+-----------+-----------+-----------+-----------+-------------+
| mni2fs                 |           | ✓         |           |           |             |
+------------------------+-----------+-----------+-----------+-----------+-------------+
| mrtools                | ✓         | ✓         | ✓\*       |           |             |
+------------------------+-----------+-----------+-----------+-----------+-------------+
| plotSurfaceROIBoundary |           | ✓         | ✓\*       |           |             |
+------------------------+-----------+-----------+-----------+-----------+-------------+
| Vistasoft              | ✓         | ✓         | ✓         |           | ✓           |
+------------------------+-----------+-----------+-----------+-----------+-------------+
Note: The tools listed contain functionality to generate at least close-to-publication-ready neuroimaging figures via user-entered code within R, MATLAB and Python environments.This list does not include cross-platform general purpose visualization software. \
\*Cortex only

@@

patchwork <- figs[[1]]/figs[[2]]|((figs[[6]]/(figs[[8]]|figs[[9]]))/figs[[7]])+plot_layout(heights = c(0.8,0.8,1.5))|((figs[[3]]/figs[[4]]/figs[[10]])+plot_layout(heights = c(0.5,1,1)))

@@

Often cerebellar and brain-stem regions are not well represented in software (e.g. Figure 1), potentially mirroring a cortico-centric sentiment that has prevailed in human neuroimaging (Chin, Chang, & Holmes). Likewise, custom non-cortical atlases such as non-standard subcortical atlas schemes is not yet straight forward, and usually require multiple functions and packages to visualize. Finally, some neuroimaging related data types, such as streamlines resulting from DWI-based tractography, are still not well represented in code-based visualization tools.

As can be seen in Table 1, there are usually multiple packages within each programming environment which are capable of visualizing each data time. While this provide choice for advanced users, it can also lead to confusion for novice users who may not be familiar with the nuanced differences between tools. Future work should continue to consolidate brain visualization methods into unified beginner-friendly tools which are capable of plotting multiple data types.

@@

# Supplement (Code used to generate Figures)

@@

#Set the breaks/intervals you want on the color bar (e.g. from .3 to .6, by intervals of 0.005)
breaks = seq(.3,.6, by=0.005)

@@

#Use the ortho2 function from the neurobase package to make the figure
ortho2(x = template,   #Specify the background template
       y = effect,     #Specify the effect you want to overlay on the tempplate
       crosshairs = F, #Remove the cross-hairs
       bg = "white",   #Make the background white 
       NA.x = T,       #Do not display NA values
       col.y= viridis::viridis(n = 500), #Select the color scale. In this case I have used the viridis scale from the viridis package. 
       xyz = c(70,50,80), #set the x y & z slice you want to visualise
       useRaster = T,     #Sometimes using Raster makes for clearer plots
       ycolorbar = TRUE,  #Add a color bar
       mfrow = c(1,1)) + 
  colorbar(breaks,col = viridis::viridis(n=length(breaks)-1), 
           text.col = "black", labels = TRUE, maxleft = 0.95)  #Set the specifications for the colorbar

@@

library(fsbrain)
library(rgl)

@@

colourmap <- colorRampPalette(viridis::viridis(n = 1000))
fsbrain.set.default.figsize(700, 700);

brain = vis.subject.morph.native(subjects_dir, 
                                subject_id, 'sulc', 
                                cortex_only = T, 
                                views=NULL, 
                                draw_colorbar = FALSE,
                                makecmap_options = list('colFn'=colourmap))

img = export(brain, draw_colorbar = FALSE, output_img = "data/fig1d.png")

### 2022-04-23 manuscript.tex
.

\author{
    Sidhant Chopra
    \thanks{Corresponding author}
   \\
    Department of Psychology \\
    Yale University \\
  CT, USA, 06511 \\
  \texttt{\href{mailto:sidhant.chopra@yale.com}{\nolinkurl{sidhant.chopra@yale.com}}} \\
   \And
    Loïc Labache
   \\
    School of Psychology \\
    Department of Psychology \\
  CT, USA, 06511 \\
  \texttt{} \\
   \And
    Edwina R Orchard
   \\
    School of Psychology \\
    Department of Psychology \\
  CT, USA, 06511 \\
  \texttt{} \\
   \And
    Avram Holmes
   \\
    School of Psychology \\
    Department of Psychology \\
  CT, USA, 06511 \\
  \texttt{} \\
  }

@@

\begin{abstract}
Add words here.
\end{abstract}

\keywords{
    Brain Visualization
   \and
    MRI Visualization
  }

@@

\hfill\break

\begin{longtable}[]{@{}lccccc@{}}
\toprule
& Voxel & Vertex & ROI & Edge & Streamlines \\
\midrule
\endhead
R & & & & & \\
ciftitools & ✓ & ✓ & ✓* & & \\
fsbrain & ✓ & ✓ & ✓* & & \\
oro.nifti & ✓ & & & & \\
neurobase & ✓ & & & & \\
ggseg & & & ✓ & & \\
brainconn & & & & ✓ & \\
Python & & & & & \\
surfice & ✓ & ✓ & ✓ & ✓ & ✓ \\
nilearn & ✓ & ✓ & ✓ & ✓ & \\
Visbrain & ✓ & ✓ & ✓ & ✓ & \\
Pycortex & ✓ & ✓ & ✓* & & \\
pySurfer & & ✓ & ✓* & & \\
Brainspace/surfplot & & ✓ & ✓* & & \\
netneurotools & & ✓ & ✓* & & \\
Brainplotlib & & ✓ & ✓* & & \\
DIPY & ✓ & & & & ✓ \\
mrivis & ✓ & & & & \\
ENIGMA toolbox & & & ✓ & & \\
ggseg & & & ✓ & & \\
graphpype & & & & ✓ & \\
MATLAB & & & & & \\
Vistasoft & ✓ & ✓ & ✓ & & ✓ \\
BrainNetViewer & ✓ & & ✓ & ✓ & \\
mrtools & ✓ & ✓ & ✓* & & \\
FieldTrip & ✓ & ✓ & & & \\
ECoG/fMRI visualization toolbox & & ✓ & ✓* & & \\
plotSurfaceROIBoundary & & ✓ & ✓* & & \\
Brainspace & & ✓ & ✓* & & \\
CandlabCore & ✓ & & ✓ & & \\
ENIGMA toolbox & & & ✓ & & \\
\bottomrule
\end{longtable}

\hfill\break

@@

Often cerebellar and brain-stem regions are not well represented in software (e.g.~Figure 1), potentially mirroring a cortico-centric sentiment that has prevailed in human neuroimaging (Chin, Chang, \& Holmes). Likewise, custom regions of interest, such as non-standard subcortical atlas schemes is not yet straight forward, and usually require multiple functions and packages to visualize. Finally, some neuroimaging related data types, such as streamlines resulting from DWI-based tractography, are still not well represented in code-based vizualistion tools.

@@

\hypertarget{supplement-code-used-to-generate-figure}{%
\subsubsection{Supplement (Code used to generate figure)}\label{supplement-code-used-to-generate-figure}}

@@

\CommentTok{\#Set the breaks/intervas you want on the color bar (e.g. from .3 to .6, by intervals of 0.005)}
\NormalTok{breaks }\OtherTok{=} \FunctionTok{seq}\NormalTok{(.}\DecValTok{3}\NormalTok{,.}\DecValTok{6}\NormalTok{, }\AttributeTok{by=}\FloatTok{0.005}\NormalTok{)}

@@

\CommentTok{\#Use the ortho2 function from the neurobase package to make the figure}
\FunctionTok{ortho2}\NormalTok{(}\AttributeTok{x =}\NormalTok{ template,   }\CommentTok{\#Specify the background template}
       \AttributeTok{y =}\NormalTok{ effect,     }\CommentTok{\#Specify the effect you want to overlay on the tempplate}
       \AttributeTok{crosshairs =}\NormalTok{ F, }\CommentTok{\#Remove the cross{-}hairs}
       \AttributeTok{bg =} \StringTok{"white"}\NormalTok{,   }\CommentTok{\#Make the background white }
       \AttributeTok{NA.x =}\NormalTok{ T,       }\CommentTok{\#Do not display NA values}
       \AttributeTok{col.y=}\NormalTok{ viridis}\SpecialCharTok{::}\FunctionTok{viridis}\NormalTok{(}\AttributeTok{n =} \DecValTok{500}\NormalTok{), }\CommentTok{\#Select the colour scale. In this case I have used the viridis scale from the viridis package. }
       \AttributeTok{xyz =} \FunctionTok{c}\NormalTok{(}\DecValTok{70}\NormalTok{,}\DecValTok{50}\NormalTok{,}\DecValTok{80}\NormalTok{), }\CommentTok{\#set the x y \& z slice you want to visualise}
       \AttributeTok{useRaster =}\NormalTok{ T,   }\CommentTok{\#Sometimes using Raster makes for clearer plots}
       \AttributeTok{ycolorbar =} \ConstantTok{TRUE}\NormalTok{, }\CommentTok{\#Add a colorbar}
       \AttributeTok{mfrow =} \FunctionTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{,}\DecValTok{1}\NormalTok{)) }\SpecialCharTok{+} 
  \FunctionTok{colorbar}\NormalTok{(breaks,}\AttributeTok{col =}\NormalTok{ viridis}\SpecialCharTok{::}\FunctionTok{viridis}\NormalTok{(}\AttributeTok{n=}\FunctionTok{length}\NormalTok{(breaks)}\SpecialCharTok{{-}}\DecValTok{1}\NormalTok{), }
           \AttributeTok{text.col =} \StringTok{"black"}\NormalTok{, }\AttributeTok{labels =} \ConstantTok{TRUE}\NormalTok{, }\AttributeTok{maxleft =} \FloatTok{0.95}\NormalTok{)  }\CommentTok{\#Set the specifications for the colorbar}

@@

\FunctionTok{library}\NormalTok{(fsbrain)}

@@

\NormalTok{colourmap }\OtherTok{\textless{}{-}} \FunctionTok{colorRampPalette}\NormalTok{(viridis}\SpecialCharTok{::}\FunctionTok{viridis}\NormalTok{(}\AttributeTok{n =} \DecValTok{10000}\NormalTok{))}
\FunctionTok{fsbrain.set.default.figsize}\NormalTok{(}\DecValTok{700}\NormalTok{, }\DecValTok{700}\NormalTok{);}

\NormalTok{cm }\OtherTok{=} \FunctionTok{vis.subject.morph.standard}\NormalTok{(subjects\_dir, }
\NormalTok{                                subject\_id, }\StringTok{\textquotesingle{}sulc\textquotesingle{}}\NormalTok{, }
                                \AttributeTok{fwhm=}\StringTok{\textquotesingle{}10\textquotesingle{}}\NormalTok{, }
                                \AttributeTok{cortex\_only =}\NormalTok{ T, }
                                \AttributeTok{views=}\ConstantTok{NULL}\NormalTok{, }
                                \AttributeTok{makecmap\_options =} \FunctionTok{list}\NormalTok{(}\StringTok{\textquotesingle{}colFn\textquotesingle{}}\OtherTok{=}\NormalTok{colourmap))}
\NormalTok{img }\OtherTok{=} \FunctionTok{export}\NormalTok{(cm, }\AttributeTok{colorbar\_legend=}\StringTok{\textquotesingle{}Effect\textquotesingle{}}\NormalTok{, }\AttributeTok{output\_img =} \StringTok{"data/fig1d.png"}\NormalTok{)}

\FunctionTok{rgl.snapshot}\NormalTok{(}\StringTok{"data/fig1d.png"}\NormalTok{)}
\FunctionTok{rgl.close}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

>>>>

\author{
    Sidhant Chopra
    \thanks{Corresponding author}
   \\
    Department of Psychology \\
    Yale University \\
  CT, USA, 06511 \\
  \texttt{\href{mailto:sidhant.chopra@yale.com}{\nolinkurl{sidhant.chopra@yale.com}}} \\
   \And
    Loïc Labache
   \\
    Department of Psychology \\
    Yale University \\
  CT, USA, 06511 \\
  \texttt{} \\
   \And
    Edwina R Orchard
   \\
    Department of Psychology \\
    Yale University \\
  CT, USA, 06511 \\
  \texttt{} \\
   \And
    Avram Holmes
   \\
    Department of Psychology \\
    Yale University \\
  CT, USA, 06511 \\
  \texttt{} \\
  }

@@

\begin{abstract}

\end{abstract}

\keywords{
    Neuroimaging visualization
   \and
    Reproducibility
   \and
    Programmatic figures
   \and
    Open Science
   \and
    R
  }

@@

\hfill\break
\textbf{Table 1. Examples of code-based neuroimaging visualizations tools that can be accessed directly within R, MATLAB and Python environments.}

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.29}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.14}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.14}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.14}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.14}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.16}}@{}}
\toprule
& Voxel & Vertex & ROI & Edge & Streamlines \\
\midrule
\endhead
\textbf{R} & & & & & \\
ANTsR & ✓ & ✓ & ✓ & & \\
brainconn & & & & ✓ & \\
brainR & ✓ & & ✓ & & \\
ciftitools & ✓ & ✓ & ✓* & & \\
fsbrain & ✓ & ✓ & ✓* & & \\
ggseg & & & ✓ & & \\
neurobase & ✓ & & & & \\
oro.nifti & ✓ & & & & \\
\textbf{Python} & & & & & \\
ANTsPy & ✓ & ✓ & ✓ & & \\
brainiak & ✓ & & & & \\
Brainplotlib & & ✓ & ✓* & & \\
Brainspace/surfplot & & ✓ & ✓* & & \\
DIPY & ✓ & & & & ✓ \\
ENIGMA toolbox & & & ✓ & & \\
FSLeyes & ✓ & ✓ & ✓ & & \\
ggseg & & & ✓ & & \\
graphpype & & & & ✓ & \\
MMVT & & ✓ & ✓ & ✓ & \\
MNE & ✓ & ✓ & ✓ & & \\
mrivis & ✓ & & & & \\
NaNSlice & ✓ & & & & \\
netneurotools & & ✓ & ✓* & & \\
nilearn & ✓ & ✓ & ✓ & ✓ & \\
niwidget & ✓ & ✓ & & & ✓ \\
Pycortex & ✓ & ✓ & ✓* & & \\
pySurfer & & ✓ & ✓* & & \\
surfice & ✓ & ✓ & ✓ & ✓ & ✓ \\
surfplot & & ✓ & ✓ & & \\
Visbrain & ✓ & ✓ & ✓ & ✓ & \\
\textbf{MATLAB} & & & & & \\
BrainNetViewer & ✓ & & ✓ & ✓ & \\
Brainspace & & ✓ & ✓* & & \\
Brainstorm & ✓ & ✓ & ✓ & & \\
bspmview & ✓ & & ✓ & & \\
CandlabCore & ✓ & & ✓ & & \\
ECoG/fMRI Vis toolbox & & ✓ & ✓* & & \\
ENIGMA toolbox & & & ✓ & & \\
FieldTrip & ✓ & ✓ & & & \\
Lead-DBS & ✓ & & ✓ & & \\
mni2fs & & ✓ & & & \\
mrtools & ✓ & ✓ & ✓* & & \\
plotSurfaceROIBoundary & & ✓ & ✓* & & \\
Vistasoft & ✓ & ✓ & ✓ & & ✓ \\
\bottomrule
\end{longtable}

Note: The tools listed contain functionality to generate at least close-to-publication-ready neuroimaging figures via user-entered code within R, MATLAB and Python environments.This list does not include cross-platform general purpose visualization software.\\
*Cortex only

@@

Often cerebellar and brain-stem regions are not well represented in software (e.g.~Figure 1), potentially mirroring a cortico-centric sentiment that has prevailed in human neuroimaging (Chin, Chang, \& Holmes). Likewise, custom non-cortical atlases such as non-standard subcortical atlas schemes is not yet straight forward, and usually require multiple functions and packages to visualize. Finally, some neuroimaging related data types, such as streamlines resulting from DWI-based tractography, are still not well represented in code-based visualization tools.

As can be seen in Table 1, there are usually multiple packages within each programming environment which are capable of visualizing each data time. While this provide choice for advanced users, it can also lead to confusion for novice users who may not be familiar with the nuanced differences between tools. Future work should continue to consolidate brain visualization methods into unified beginner-friendly tools which are capable of plotting multiple data types.

@@

\hypertarget{supplement-code-used-to-generate-figures}{%
\section{Supplement (Code used to generate Figures)}\label{supplement-code-used-to-generate-figures}}

@@

\CommentTok{\#Set the breaks/intervals you want on the color bar (e.g. from .3 to .6, by intervals of 0.005)}
\NormalTok{breaks }\OtherTok{=} \FunctionTok{seq}\NormalTok{(.}\DecValTok{3}\NormalTok{,.}\DecValTok{6}\NormalTok{, }\AttributeTok{by=}\FloatTok{0.005}\NormalTok{)}

@@

\CommentTok{\#Use the ortho2 function from the neurobase package to make the figure}
\FunctionTok{ortho2}\NormalTok{(}\AttributeTok{x =}\NormalTok{ template,   }\CommentTok{\#Specify the background template}
       \AttributeTok{y =}\NormalTok{ effect,     }\CommentTok{\#Specify the effect you want to overlay on the tempplate}
       \AttributeTok{crosshairs =}\NormalTok{ F, }\CommentTok{\#Remove the cross{-}hairs}
       \AttributeTok{bg =} \StringTok{"white"}\NormalTok{,   }\CommentTok{\#Make the background white }
       \AttributeTok{NA.x =}\NormalTok{ T,       }\CommentTok{\#Do not display NA values}
       \AttributeTok{col.y=}\NormalTok{ viridis}\SpecialCharTok{::}\FunctionTok{viridis}\NormalTok{(}\AttributeTok{n =} \DecValTok{500}\NormalTok{), }\CommentTok{\#Select the color scale. In this case I have used the viridis scale from the viridis package. }
       \AttributeTok{xyz =} \FunctionTok{c}\NormalTok{(}\DecValTok{70}\NormalTok{,}\DecValTok{50}\NormalTok{,}\DecValTok{80}\NormalTok{), }\CommentTok{\#set the x y \& z slice you want to visualise}
       \AttributeTok{useRaster =}\NormalTok{ T,     }\CommentTok{\#Sometimes using Raster makes for clearer plots}
       \AttributeTok{ycolorbar =} \ConstantTok{TRUE}\NormalTok{,  }\CommentTok{\#Add a color bar}
       \AttributeTok{mfrow =} \FunctionTok{c}\NormalTok{(}\DecValTok{1}\NormalTok{,}\DecValTok{1}\NormalTok{)) }\SpecialCharTok{+} 
  \FunctionTok{colorbar}\NormalTok{(breaks,}\AttributeTok{col =}\NormalTok{ viridis}\SpecialCharTok{::}\FunctionTok{viridis}\NormalTok{(}\AttributeTok{n=}\FunctionTok{length}\NormalTok{(breaks)}\SpecialCharTok{{-}}\DecValTok{1}\NormalTok{), }
           \AttributeTok{text.col =} \StringTok{"black"}\NormalTok{, }\AttributeTok{labels =} \ConstantTok{TRUE}\NormalTok{, }\AttributeTok{maxleft =} \FloatTok{0.95}\NormalTok{)  }\CommentTok{\#Set the specifications for the colorbar}

@@

\FunctionTok{library}\NormalTok{(fsbrain)}
\FunctionTok{library}\NormalTok{(rgl)}

@@

\NormalTok{colourmap }\OtherTok{\textless{}{-}} \FunctionTok{colorRampPalette}\NormalTok{(viridis}\SpecialCharTok{::}\FunctionTok{viridis}\NormalTok{(}\AttributeTok{n =} \DecValTok{1000}\NormalTok{))}
\FunctionTok{fsbrain.set.default.figsize}\NormalTok{(}\DecValTok{700}\NormalTok{, }\DecValTok{700}\NormalTok{);}

\NormalTok{brain }\OtherTok{=} \FunctionTok{vis.subject.morph.native}\NormalTok{(subjects\_dir, }
\NormalTok{                                subject\_id, }\StringTok{\textquotesingle{}sulc\textquotesingle{}}\NormalTok{, }
                                \AttributeTok{cortex\_only =}\NormalTok{ T, }
                                \AttributeTok{views=}\ConstantTok{NULL}\NormalTok{, }
                                \AttributeTok{draw\_colorbar =} \ConstantTok{FALSE}\NormalTok{,}
                                \AttributeTok{makecmap\_options =} \FunctionTok{list}\NormalTok{(}\StringTok{\textquotesingle{}colFn\textquotesingle{}}\OtherTok{=}\NormalTok{colourmap))}

\NormalTok{img }\OtherTok{=} \FunctionTok{export}\NormalTok{(brain, }\AttributeTok{draw\_colorbar =} \ConstantTok{FALSE}\NormalTok{, }\AttributeTok{output\_img =} \StringTok{"data/fig1d.png"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}
